Are We Teaching Cybersecurity (and how well)?\\(Abstract 20 January, Paper 27th)

### 2019-01-11 ITiCSE2019.tex
Tom's IET source

Cybersecurity has been in the news for several years, generally prompted by spectacular breaches of one kind or another, such as \cite{BritishAirways2018a}.

>>>>

Cybersecurity has been in the news for several years, generally prompted by spectacular breaches of one kind or another, such as \cite{BritishAirways2018a}.
It needs attention across the spectrum:
\begin{quote}
change the culture in your organisation around cyber security; to t ry to do for cyber what has been done so successfully for health and safety, for example, over the last ten years - to get everybody to take it seriously; to take the risk management process seriously and drive that down through the organisation. \cite{Hannigan2019a}
\end{quote}
